### 2017-08-12 src/4_OnlineLearning.tex
comentarios cap 3 finalizados

\begin{eqnarray*}
 V & \rightarrow & \mathbb{R}^+ \\
  (f(x), y) &\rightarrow & V(f(x),y)
\end{eqnarray*}

@@

If we have a learning model $\hat{f}$, its expected generalisation error on a
testing sample $x$ can be decomposed as shown in equation \ref{eq:bvtrade} (demo
in \cite{geman1992neural}):

@@

This bias-variance tradeoff is the reason why, in order to obtain the best model,
data is usually broken in three subsets: training set, validation set and
testing set. Training set is used to determine the model, validation set is used
to estimate the generalisation error and finally testing set is used to estimate
the accuracy of the model. Usually the partition is 50\% for training set, 25\%
for validation and 25\% for testing purposes. This procedure can be extended to
a Cross Validation (CV) procedure \cite{geisser1975}, usually used when the
amount of data is limited. Various splitting strategies lead to various CV
estimates. In K-fold cross-validation the training data is divided randomly into
K distinct subsets, then the network is trained using K-1 subsets, and tested on
the remaining subset. The process of training and testing is then repeated for
each of the K possible choices of the subset omitted from the training. The
average performance on the K omitted subsets is then our estimate of the
generalisation performance.

Another way to control the complexity of the model is to include in the
optimisation function not only the generalisation error but a penalisation of
high complex models.

%=======================HASTA ACA REVISADO PROFE =========================
\subsection{Regularization}\label{sec:regularization}

Regularization can be understood using two contexts: learning theory
(probabilistic) and inverse problems (deterministic). In the context of
learning, regularization refers to techniques allowing to avoid over-fitting and
the desire property of the selected estimator is to perform well on new data (to
generalize), e.g. regularized least squares. In the context of inverse problems,
regularization objective is to stabilise, with respect to noise, a possibly
ill-conditioned matrix inversion problem e.g spectral cut-off and Tikhonov
regularization or ridge regression (RR)\cite{ tikhonov1977}.

@@

Tikhonov introduced a regularisation which ensures well-posedness and
generalisation of ERM, i.e prevents overfit, by constraining the hypothesis
space $\mathcal{H}$ usually called regularised ERM or Tikhonov regularisation.

Tikhonov regularisation minimised over the hypothesis space $\mathcal{H}$ for a
fixed positive parameter $\lambda$ the following:

\begin{equation} 
\label{eq:rerm}
R_{\text{emp}}[f] = \frac{1}{n} \sum_{i=1}^n V(f(x),y) + \lambda \mathcal{R}(f)
\end{equation}

\noindent where $\mathcal{R}(f)$ is the regulariser, a penalisation on $f$.

@@

Ridge regression was independently proposed by Tikhonov \cite{tikhonov1963} and
Phillips \cite{phillips1962}. 
One example of regularisation in linear models is Ridge Regression (RR), which is a regularised least squares method.
The least squares (LS) method is a well known way to solve a regression
problem. 
LS method consists of minimising the sum of squared errors:

\begin{eqnarray*}
\label{eq:lsm}
 J(\mathbf{X}) =& \displaystyle \sum_{t=1}^N (f(\mathbf{x}_t)-y_t)^2 \\
 =&\displaystyle \sum_{t=1}^N (\mathbf{\mathbf{X}}^\top {\mathbf{x}}_t-y_t)^2 \\
 =& \| \mathbf{A}\mathbf{\mathbf{X}} - \mathbf{Y} \|_2^2 
\end{eqnarray*}

\noindent which is equivalent to find a solution to 
\begin{equation}
\label{eq:regproblem}
\underset{m \times n}{\mathbf{A}} \enskip \underset{n \times
l}{\mathbf{\mathbf{X}}} = \underset{m \times l}{\mathbf{Y}}
\end{equation}

@@

\textbf{Demo}\quad

To solve equation~(\ref{eq:pseudoinverse}) is equivalent to solve the following
optimisation problem:

\begin{equation}
\label{eq:RRproblem2}
\underset{\mathbf{X}(\lambda)}{\text{min}} \quad \|
\mathbf{C}\mathbf{\mathbf{X}} - \mathbf{F} \|_2^2
\end{equation}

\begin{equation*}
	\mathbf{C}=
	\begin{bmatrix} \quad &\mathbf{A}& \quad \\ \hdashline \quad
& \sqrt\lambda\mathbb{I}&\quad  
\end{bmatrix} 
\quad \text{and} \quad
	\mathbf{F}=\begin{bmatrix} \quad &\mathbf{Y}& \quad \\ \hdashline \quad
& \mathbf{0}&\quad  \end{bmatrix} \, .
\end{equation*}

Applying equation~(\ref{eq:MP}) and considering that $\mathbf{C}^\top
\mathbf{C} = \mathbf{A}^\top \mathbf{A} + \lambda \mathbb{I}$ and 
$\mathbf{C}^\top \mathbf{F}=\mathbf{A}^\top \mathbf{Y} $ we have:

\begin{eqnarray*}
\mathbf{X}(\lambda)&=&(\mathbf{C}^\top
\mathbf{C})^{-1}\mathbf{C}^\top \mathbf{F} \\
&=& (\mathbf{A}^\top \mathbf{A} + \lambda \mathbb{I})^{-1} \mathbf{A}^\top \mathbf{Y}
\end{eqnarray*}

@@

\textbf{Demo}\quad

@@

The method is called ridge regression because the term $\lambda \mathbb{I}$ adds positive entries along the diagonal (ridge) to avoid the
singularity of the covariance matrix $\mathbf{A}^\top \mathbf{A}$. This addition ensures that all of the covariance matrix eigenvalues will be strictly greater than 0, i.e the solution becomes unique.

@@

\subsection{Generalized Cross Validation}
Since we don't know the data we want to predict, the bias-variance tradeoff is not directly useful to determine $\lambda$. Many techniques have been developed to determine a suitable value for the regularization parameter. However, when no information is available on the error, one of the most popular techniques is the Generalized Cross Validation (GCV) \cite{bauer2011}. 
GCV originates from the older method leave-one-out Cross Validation \cite{stone1974}.

The leave-one-out cross validation method determine a regularization parameter that minimises the average of the squared predictions errors using each solution to predict the missing data value.

@@

\newpage

>>>>

\begin{eqnarray}
\label{eq:lossfunction}
 V & \rightarrow & \mathbb{R}^+ \\
  (f(x), y) &\rightarrow & V(f(x),y)
\end{eqnarray}

@@

If we have a learning model $\hat{f}$, its expected generalisation error on a
testing sample $x$ can be decomposed as shown in equation \ref{eq:bvtrade} (proof
in \cite{geman1992neural}):

@@

\subsection{Generalised Cross Validation}
This bias-variance tradeoff is the reason why the 
data is usually divided in three subsets: training, validation and
testing set. The training set is used to construct the model, the validation set
to estimate the generalisation error and finally the testing set to estimate
the accuracy of the model. Usually the partition is 50\% for training, 25\%
for validation and 25\% for testing purposes. When the
amount of data is limited, this procedure can be extended to
a Cross Validation (CV) approach \cite{geisser1975} . Various splitting strategies lead to various CV
estimates. In K-fold cross-validation  \cite{stone1974} the training data is divided randomly into
K distinct subsets, then the model is trained using K-1 subsets, and tested on
the remaining subset. The process of training and testing is then repeated for
each of the K possible choices of the subset omitted from the training. The
average performance on the K omitted subsets is the estimate of the
generalisation performance.

%Another way to control the complexity of the model is to include in the
%optimisation function not only the generalisation error but a penalisation of
%high complex models.

%Since we don't know the data we want to predict, the bias-variance tradeoff is not directly useful to determine $\lambda$. Many techniques have been developed to determine a suitable value for the regularization parameter. However, when no information is available on the error, one of the most popular techniques is the Generalized Cross Validation (GCV) \cite{bauer2011}. GCV originates from the older method leave-one-out Cross Validation.

%The leave-one-out cross validation method determine a regularization parameter that minimises the average of the squared predictions errors using each solution to predict the missing data value.

\subsection{Regularization}\label{sec:regularization}

Regularization can be understood using two contexts: learning theory
(probabilistic) and inverse problems (deterministic). In the context of
learning, regularization refers to techniques allowing to avoid over-fitting and
the desire property of the selected estimator is to perform well on new data (to
generalize), e.g. regularized least squares. In the context of inverse problems,
regularization objective is to stabilise, with respect to noise, a possibly
ill-conditioned matrix inversion problem e.g spectral cut-off and Tikhonov
regularization or ridge regression (RR) \cite{ tikhonov1977}.

@@

Tikhonov introduced a regularization which ensures well-posedness and
generalisation of ERM, i.e prevents overfit, by constraining the hypothesis
space $\mathcal{H}$ usually called regularised ERM or Tikhonov regularisation.

%Tikhonov regularisation minimised over the hypothesis space $\mathcal{H}$ for a
%fixed positive parameter $\lambda$ the following:
Tikhonov regularisation considers a functional of the form:

\begin{equation} 
\label{eq:rerm}
R_{\text{emp}}[f] = \frac{1}{n} \sum_{i=1}^n V(f(x_i),y_i) + \lambda \mathcal{R}(f)
\end{equation}

\noindent where $X \subseteq \mathbb{R}^m$ and $Y = \mathbb{R}$ , $V$ is the loss function defined in the equation \ref{eq:lossfunction} and $\mathcal{R}(f)$ is the regulariser, a penalisation on $f$. One example of regularisation in linear models is Ridge Regression (RR), which is a regularised least squares method.

@@

Ridge regression (RR) was independently proposed by Tikhonov \cite{tikhonov1963} and
Phillips \cite{phillips1962}. RR corresponds to a regularised least squares method. The least squares (LS) method is a well known way to solve a regression
problem. LS method consists of minimising the sum of squared errors:

\begin{eqnarray*}
\label{eq:lsm}
 J(\mathbf{X}) =& \displaystyle \sum_{t=1}^N (f(\mathbf{x}_t)-y_t)^2 \\
 =&\displaystyle \sum_{t=1}^N (\mathbf{\mathbf{A}}^\top {\mathbf{x}}_t-y_t)^2 \\
 =& \| \mathbf{A}\mathbf{\mathbf{X}} - \mathbf{Y} \|_2^2 
\end{eqnarray*}

\noindent where $f(\mathbf{x}_t)={\mathbf{A}}^\top {\mathbf{x}}_t$. To solve equation \ref{eq:lsm} is equivalent to find a solution of:
\begin{equation}
\label{eq:regproblem}
\underset{m \times n}{\mathbf{A}} \enskip \underset{n \times
l}{\mathbf{\mathbf{X}}} = \underset{m \times l}{\mathbf{Y}}
\end{equation}

@@

%\textbf{Demo}\quad
%
%To solve equation~(\ref{eq:pseudoinverse}) is equivalent to solve the following
%optimisation problem:
%
%
%\begin{equation}
%\label{eq:RRproblem2}
%\underset{\mathbf{X}(\lambda)}{\text{min}} \quad \|
%\mathbf{C}\mathbf{\mathbf{X}} - \mathbf{F} \|_2^2
%\end{equation}
%
%\noindent where
%
%\begin{equation*}
%	\mathbf{C}=
%	\begin{bmatrix} \quad &\mathbf{A}& \quad \\ \hdashline \quad
%& \sqrt\lambda\mathbb{I}&\quad  
%\end{bmatrix} 
%\quad \text{and} \quad
%	\mathbf{F}=\begin{bmatrix} \quad &\mathbf{Y}& \quad \\ \hdashline \quad
%& \mathbf{0}&\quad  \end{bmatrix} \, .
%\end{equation*}
%
%Applying equation~(\ref{eq:MP}) and considering that $\mathbf{C}^\top
%\mathbf{C} = \mathbf{A}^\top \mathbf{A} + \lambda \mathbb{I}$ and 
%$\mathbf{C}^\top \mathbf{F}=\mathbf{A}^\top \mathbf{Y} $ we have:
%
%\begin{eqnarray*}
%\mathbf{X}(\lambda)&=&(\mathbf{C}^\top
%\mathbf{C})^{-1}\mathbf{C}^\top \mathbf{F} \\
%&=& (\mathbf{A}^\top \mathbf{A} + \lambda \mathbb{I})^{-1} \mathbf{A}^\top \mathbf{Y}
%\end{eqnarray*}
%
%$\blacksquare$

@@

\textbf{Proof}\quad

@@

The method is called ridge regression because the term $\lambda \mathbb{I}$ adds positive entries along the diagonal (ridge) to avoid the
singularity of the covariance matrix $\mathbf{A}^\top \mathbf{A}$. This addition ensures that all of the covariance matrix eigenvalues will be strictly greater than 0, i.e the solution becomes unique.
%=======================HASTA ACA REVISADO PROFE =========================

@@

@@
